### 2022-06-03 tail/appendix.tex
Add files via upload

\chapter{Appendix to Chapter 1}
\section{Relation between $g_{it}(\tau)$ and $\psi_{it}(\tau)$}

@@

\section{Computation of $\psi_{it}(\tau) \tau$}

@@

\section{Likelihood function}
\label{appendix1}

@@

\section{Distance-to-Default estimation}
\label{appendix2}

\subsection{Distance-to-default}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=6in]{DTD_Crosbie_Bohn.JPG} 
\caption{Distance-to-default} 
\label{fig:DD}
\end{figure}

\subsection{Variance restriction method to estimate DtD}
The variance restriction method is used in \citet{DSW} to estimate the distance-to-default (DtD). This method is based on \citet{Merton1974} model which states that firm's equity value can be seen as a call option on the underlying asset and the strike being the amount of debt. This holds because stockholders receive money only once debt holders are fully paid. \\
Applying the Black-Scholes call option formula to equity value, we get the following :
\begin{equation*}
\left\{
  \begin{array}{lll}
    V_E & = & V_A N(d_1) - e^{-r(T-t)} \cdot D \cdot N(d_2)\\
    d_1 & = & \dfrac{\dfrac{V_A}{D}+(r-\dfrac{\sigma_A^2}{2}(T-t)}{\sigma_A \sqrt{T-t}} \\
    d_2 & = & d_1 - \sigma_A \sqrt{T-t}.
  \end{array}
\right.
\end{equation*}
Where $V_E$ is the market equity value, $V_A$ is the market asset value, D is the default point and N the normal cumulative distribution function. Following KMV assumption, the default point D in the variance restriction method is specified as short-term debt plus one half of long-term debt.\\
Using It\^o, we can show that 
\begin{equation*}
\sigma_E = \dfrac{V_A}{V_E}\cdot \frac{\partial V_E}{\partial V_A}\cdot \sigma_A.
\end{equation*}
Hence, the method consists of solving the following system with two equations and two unknowns $V_A$ and $\sigma_A$ :
\begin{equation*}
\left\{
  \begin{array}{lll}
    V_E & = & V_A N(d_1) - e^{-r(T-t)} \cdot D \cdot N(d_2)\\
    \sigma_E & = & \dfrac{V_A}{V_E}\cdot \frac{\partial V_E}{\partial V_A}\cdot \sigma_A,
  \end{array}
\right.
\end{equation*}
Once $V_A$ and $\sigma_A$ are estimated, the DtD is defined as the distance between the expected value of the asset and the default point. After substitution in a normal CDF, we get
\begin{equation}
DtD = \dfrac{\ln(\dfrac{V_A}{L})+(\mu-\dfrac{\sigma_A^2}{2})(T-t)}{\sigma_A \sqrt{T-t}}.
\end{equation}
However, many papers agree to say that $\mu$ is very tedious to estimate. Hence, DtD is often computed as
\begin{equation}
DtD = \dfrac{\ln(\dfrac{V_A}{L})}{\sigma_A \sqrt{T-t}}.
\end{equation}

@@

\subsection{Maximum likelihood estimation to estimate DtD}

@@

\chapter{Appendix to Chapter 2}
\section{Technical proofs}
\subsection{Proof of Lemma \ref{lemma:small}}
From the definition of DIG, we know that for any $R_k\not\in\mathcal{PA}_j$, 
$
 I(R_k\rightarrow R_j||\mathcal{R}_{-\{k,j\}})=0   
$. 
This implies that for all $t$, 
\begin{align}\label{eq:app_l1}
     p(R_{j,t}|\mathcal{R}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{k\}}^{t-1}).
\end{align}
On the other hand, by the assumption of the Lemma, $R_i\not\in\mathcal{PA}_j$, we have
\begin{align}\label{eq:app_ll2}
 I(R_i\rightarrow R_j||\mathcal{R}_{-\{i,j\}})=0,  
\end{align}
or equivalently, for all $t$,
\begin{align}\label{eq:app_p1}
     p(R_{j,t}|\mathcal{R}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1}).
\end{align}
 Combining \eqref{eq:app_l1} and \eqref{eq:app_p1} imply that for any pair $\{R_i,R_k\}$ that are not in the parent set of $R_j$, we have
\begin{align}\label{eq:app_l1_2}
   p(R_{j,t}|\mathcal{R}_{-\{k\}}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1}).
\end{align}
To prove the claim of this lemma, we use \eqref{eq:app_l1_2} to show that all the time series in $\mathcal{R}_{-\{i,j\}}\setminus\mathcal{C}$ can be removed from the conditioning in \eqref{eq:app_ll2}. 
Let $R_k\in \mathcal{R}_{-\{i,j\}}\setminus\mathcal{C}$, by multiplying the above equality with $p(R_{i}^{t-1}|\mathcal{R}_{-\{i,k\}}^{t-1})$ and marginalizing over $R_{i}^{t-1}$, we obtain
\begin{align*}
    &\int p(R_{j,t}|\mathcal{R}_{-\{k\}}^{t-1})p(R_{i}^{t-1}|\mathcal{R}_{-\{i,k\}}^{t-1})dR_i^{t-1}=p(R_{j,t}|\mathcal{R}_{-\{i,k\}}^{t-1})\\
    &=\int p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1})p(R_{i}^{t-1}|\mathcal{R}_{-\{i,k\}}^{t-1})dR_i^{t-1}=p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1}).
\end{align*}
The above equalities and \eqref{eq:app_p1} imply that for all $t$,
\begin{align*}
p(R_{j,t}|\mathcal{R}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{i,k\}}^{t-1}),    
\end{align*}
or equivalently,  
\begin{align*}
    I(R_i\rightarrow R_j||\mathcal{R}_{-\{i,j,k\}})=0.
\end{align*}
By repeating the above procedure, we obtain
\begin{align*}
    I(R_i\rightarrow R_j||\mathcal{C})=0.
\end{align*}

\subsection{Proof of Lemma \ref{lemma:lin}}
Consider the VAR model in \eqref{eq:linearsys}. 
First, we assume that $X_i$ has no influence on $X_j$, i.e., $I(X_i\rightarrow X_j||\mathcal{X}_{-\{i,j\}})=0$ or equivalently $a_{j,i}=0$ and show that \eqref{eq:lemma_linear} holds. Given this assumption, we have that for all $t$,
\begin{align*}
    &p(X_{j,t}|\mathcal{X}_{-\{i\}}^{t-1})=p(X_{j,t}|\mathcal{X}^{t-1}).
\end{align*}
Using the equations in \eqref{eq:linearsys} and the assumption that $a_{j,i}=0$, we obtain
\begin{align*}
    &p(X_{j,t}|\mathcal{X}^{t-1})= p(N_{j,t}+\sum_{k}a_{j,k}X_{k,t-1}|\mathcal{X}^{t-1})=p(N_{j,t}+\sum_{k\neq i}a_{j,k}X_{k,t-1}|\mathcal{X}^{t-1})\\ 
    &=p(N_{j,t}+\sum_{k\neq i}a_{j,k}X_{k,t-1}|\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{i}^{t-1},{X}_{j}^{t-1})\\
    &=p(N_{j,t}+\sum_{k\neq i}a_{j,k}X_{k,t-1}|\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{j}^{t-1}).
\end{align*}
Note that we could replace $\mathcal{X}^{t-1}$ by $\{\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{i}^{t-1},{X}_{j}^{t-1}\}$ or\\
$\{\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{j}^{t-1}\}$ in the above equations, because given either of them $\sum_{k\neq i}a_{j,k}X_{k,t-1}$ becomes a constant and independent of $N_{j,t}$.
By defining $Q_{t-1}:=\sum_{k\neq i}a_{j,k}X_{k,t-1}$, the above equations can be rewritten as follows 
\begin{align*}
    &p(X_{j,t}|\mathcal{X}^{t-1})=p(X_{j,t}|Q_{t-1},{X}_{i}^{t-1},{X}_{j}^{t-1})=p(X_{j,t}|Q_{t-1},{X}_{j}^{t-1}), \forall t,
\end{align*}
or equivalently, 
\begin{align*}
    &\mathbb{E}\left[\log\frac{p(X_{j,t}|Q_{t-1},{X}_{i}^{t-1},{X}_{j}^{t-1})}{p(X_{j,t}|Q_{t-1},{X}_{j}^{t-1})}\right]=0, \forall t.
\end{align*}
Using the definition of DI, the above equalities can be written in terms of DI as follows
\begin{align*}
   I(X_i\rightarrow X_j||Q)=0.
\end{align*}
On the other hand, we have 
\begin{align*}
&[a_{j,1},...,a_{j,i-1},a_{j,i+1},...,a_{j,m}]=\arg\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||X_{j,t}- \textbf{w}^T \textbf{X}_{-\{i\},t-1}||_2^2\right]:=\textbf{u}_t.
\end{align*}
where $\textbf{X}_{-\{i\},t-1} :=[X_{1,t-1},..., X_{i-1,t-1}, X_{i+1,t-1},..., X_{m,t-1} ]^T$. This means that $Q_{t-1}=\textbf{u}_t^T\textbf{X}_{-\{i\},t-1}$.

@@

\subsection{Proof of Lemma \ref{lemma:nonlinear}}
The proof is similar to the linear version and uses the fact that exogenous noises $\{\varepsilon_{j,t}\}$ are independent. More precisely, we have  
\begin{align*}
    &p(X_{j,t}|\mathcal{X}^{t-1})=p(F_{j}(\mathcal{X}^{t-1}) + \varepsilon_{j,t}|F_{j}(\mathcal{X}^{t-1})).
\end{align*}
Since there is no influence from $X_i$ to $X_j$, we can eliminate it from the conditioning and the argument of function $F_j$ and obtain
\begin{align*}
&p\big(F_{j}(\mathcal{X}^{t-1}) + \varepsilon_{j,t}|\mathcal{X}^{t-1}\big)=p\big(F_{j}(\mathcal{X}_{-\{i\}}^{t-1}) + \varepsilon_{j,t}|\mathcal{X}_{-\{i\}}^{t-1}\big).
\end{align*}
On the other hand, because given either $\{F_{j}(\mathcal{X}_{-\{i\}}^{t-1}), X_i^{t-1},X_j^{t-1}\}$ or \\
$\{F_{j}(\mathcal{X}_{-\{i\}}^{t-1}),X_j^{t-1}\}$, the value of $F_{j}(\mathcal{X}_{-\{i\}}^{t-1})$ is no longer a random variable. Using this relationship and the fact that $\varepsilon_{j,t}$ is independent of $\mathcal{X}^{t-1}$, we obtain
\begin{small}
\begin{align*}
    &p\big(F_{j}(\mathcal{X}_{-\{i\}}^{t-1}) + \varepsilon_{j,t}|F_{j}(\mathcal{X}_{-\{i\}}^{t-1}), X_i^{t-1},X_j^{t-1}\big)=
    p\big(F_{j}(\mathcal{X}_{-\{i\}}^{t-1}) + \varepsilon_{j,t}|F_{j}(\mathcal{X}_{-\{i\}}^{t-1}), X_j^{t-1}\big).
\end{align*}
\end{small}
By defining $Q_{t-1}:=F_{j}(\mathcal{X}_{-\{i\}}^{t-1})$, the above equations can be rewritten in terms of DI as follows,
\begin{align*}
    I(X_i\rightarrow X_j||Q)=0.
\end{align*}

@@

\section{k-Nearest Neighbors estimator of mutual information}
Suppose that $N+M$ i.i.d. realizations $\{\textbf{x}_1, ..., \textbf{x}_{N+M}\}$ are available from $\PP_{X,Y,Z}$, where $\textbf{x}_i$ denotes the $i$-th realization of $(X,Y,Z)$.
The data is randomly divided into two subsets $\mathcal{S}_1$ and $\mathcal{S}_2$ of $N$ and $M$ points, respectively.  
The estimator has two main stages:
In the first stage, a k-nearest density estimator $\widehat{\PP}_{X,Y,Z}$ at the $N$ points of $\mathcal{S}_1$ is estimated using the $M$ realizations of $\mathcal{S}_2$ as follows:

@@

\section{Koopman-based Lifting Method}
Let $\textbf{X}_t:=\{X_{1,t}, ..., X_{m,t}\}$ denote a network of $m$ time series such that 
\begin{align}\label{dyn}
\dot{\textbf{X}}_t = F(\textbf{X}_t),
\end{align}
where the vector field $F(\textbf{X})=(F_1(\textbf{X}),...,F_m(\textbf{X}))$ is of the form
\begin{align}
F_j(\textbf{X})= \sum_{k=1}^K w_{j,k} h_k(\textbf{X}).
\end{align}
In the above equation, $w_{j,k}\in\mathbb{R}$ are unknown weights and $\{h_k(\textbf{X})\}$ denote a set of known library functions, e.g., monomials. 
Furthermore, let $\varphi^t(\textbf{X}_0)$ denote the solution to \eqref{dyn} associated with the initial condition $\textbf{X}_0$.

@@

\section{Ideal portfolio}
In this section, we show how the ideal portfolio is related to the coefficients of the linear system in \eqref{eq:linearsys}.  
Recall the optimization problem in Lemma \ref{lemma:lin}. 
\begin{align*}
&\textbf{u}_t:=\arg\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||X_{j,t}- \textbf{w}^T \textbf{X}_{-\{i\},t-1}||_2^2\right],\\
&\textbf{X}_{-\{i\},t-1} :=[X_{1,t-1},\cdots, X_{i-1,t-1}, X_{i+1,t-1}, \cdots, X_{m,t-1} ]^T.
\end{align*}
Consider the $j$-th Equation in \eqref{eq:linearsys}, i.e., 
\begin{align*}
    X_{j,t}=\sum_{k=1}^m a_{j,k}X_{k,t-1}+N_{j,t}.
\end{align*}
If $a_{j,i}=0$, by substituting the above equation into the optimization, we obtain
\begin{align*}
&\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}+N_{j,t}||_2^2\right]=\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||N_{j,t}||_2^2\right]\\
&+\mathbb{E}\left[||\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}||_2^2\right]+2\mathbb{E}\left[||\left(\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}\right)N_{j,t}||_2^2\right]\\
&=\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}||_2^2\right]+\mathbb{E}\left[||N_{j,t}||_2^2\right]
\end{align*}
The last equality is due to the fact $N_{j,t}$ is independent of $\{X_{k,t-1}\}$ and have zero mean. This implies that the solution is $w_k=a_{j,k}$ for $k\in\{1,...,i-1,i+1,...,m\}$.

\begin{comment}
\section*{Appendix D : Ideal portfolio}
In this section, we present the relation between the ideal portfolio defined in Lemma \ref{lemma:lin} and maximally correlated portfolio. 
We use the following notations and definitions,
\begin{itemize}
\item $r$ denotes the risk-free return (random, but known at beginning of period),
  %\item $X_j$ denotes the excess return of stock $j$ over risk-free $r$,
  \item Candidate excess returns $\textbf{R}=(R_1,\dots,R_{m-1})^T$ over risk-free $r$,
  %(all stocks but $i$ and $j$, e.g., $m=498$)
  \item Covariance matrix of $\begin{pmatrix}
    X \\ \textbf{R}
  \end{pmatrix}$ is denoted by $\mathbf{\Sigma}:=\begin{pmatrix}
    \mathbf{\Sigma}_{XX} & \mathbf{\Sigma}_{X\textbf{R}} \\ \mathbf{\Sigma}_{\textbf{R}X} & \mathbf{\Sigma}_{\textbf{RR}}
  \end{pmatrix}  $. We assume that $\mathbf{\Sigma}_{\textbf{RR}}$ is invertible.

@@

\chapter{Appendix to Chapter 3}
\section{Number of messages}
As the same information sometimes refer to several companies, users are allowed to identify more than one ticker per message.  Figure \ref{fig:histtic} shows the histogram of the number of tickers tagged per message. As the vast majority of message includes only one ticker, we only show on this plot messages referring to more than one ticker. However, many messages refer to several tickers and this creates duplicates in the database because we consider the same message for all tickers tagged in the message. Figure \ref{fig:uniq} shows the number of messages with and without double counting. In our sample, the number of messages without double counting is 76 million, as opposed to 90 million messages with double counting. Figure \ref{fig:ratio} shows the ratio between the number of messages with double counting divided by the number of messages without double counting. Throughout this paper, we only refer to the number of messages with double counting.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{hist_tic.JPG}
    \caption{Histogram of the number of tickers per message, across all messages referring to more than one ticker. The maximum number of tickers per message amounts to 28 and corresponds to 11 messages in the sample.}
    \label{fig:histtic}
\end{figure}

>>>>

\chapter{Appendix}

\section{Appendix to Chapter 1}
\subsection{Relation between $g_{it}(\tau)$ and $\psi_{it}(\tau)$}

@@

\subsection{Computation of $\psi_{it}(\tau) \tau$}

@@

\subsection{Likelihood function}
\label{appendix1}

@@

\subsection{Distance-to-Default estimation}
\label{appendix2}

\subsubsection{Distance-to-default}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=6in]{DTD_Crosbie_Bohn.JPG} 
\mycaption{Distance-to-default}{} 
\label{fig:DD}
\end{figure}

\subsubsection{Variance restriction method to estimate DtD}
The variance restriction method is used in \citet{DSW} to estimate the distance-to-default (DtD). This method is based on \citet{Merton1974} model which states that firm's equity value can be seen as a call option on the underlying asset and the strike being the amount of debt. This holds because stockholders receive money only once debt holders are fully paid. \\
Applying the Black-Scholes call option formula to equity value, we get the following :
\begin{equation*}
\left\{
  \begin{array}{lll}
    V_E & = & V_A N(d_1) - e^{-r(T-t)} \cdot D \cdot N(d_2)\\
    d_1 & = & \dfrac{\dfrac{V_A}{D}+(r-\dfrac{\sigma_A^2}{2}(T-t)}{\sigma_A \sqrt{T-t}} \\
    d_2 & = & d_1 - \sigma_A \sqrt{T-t}.
  \end{array}
\right.
\end{equation*}
Where $V_E$ is the market equity value, $V_A$ is the market asset value, D is the default point and N the normal cumulative distribution function. Following KMV assumption, the default point D in the variance restriction method is specified as short-term debt plus one half of long-term debt.\\
Using It\^o, we can show that 
\begin{equation*}
\sigma_E = \dfrac{V_A}{V_E}\cdot \frac{\partial V_E}{\partial V_A}\cdot \sigma_A.
\end{equation*}
Hence, the method consists of solving the following system with two equations and two unknowns $V_A$ and $\sigma_A$ :
\begin{equation*}
\left\{
  \begin{array}{lll}
    V_E & = & V_A N(d_1) - e^{-r(T-t)} \cdot D \cdot N(d_2)\\
    \sigma_E & = & \dfrac{V_A}{V_E}\cdot \frac{\partial V_E}{\partial V_A}\cdot \sigma_A,
  \end{array}
\right.
\end{equation*}
Once $V_A$ and $\sigma_A$ are estimated, the DtD is defined as the distance between the expected value of the asset and the default point. After substitution in a normal CDF, we get
\begin{equation}
DtD = \dfrac{\ln(\dfrac{V_A}{L})+(\mu-\dfrac{\sigma_A^2}{2})(T-t)}{\sigma_A \sqrt{T-t}}.
\end{equation}
However, many papers agree to say that $\mu$ is very tedious to estimate. Hence, DtD is often computed as
\begin{equation}
DtD = \dfrac{\ln(\dfrac{V_A}{L})}{\sigma_A \sqrt{T-t}}.
\end{equation}

@@

\subsubsection{Maximum likelihood estimation to estimate DtD}

@@

\section{Appendix to Chapter 2}
\subsection{Technical proofs}
\subsubsection{Proof of Lemma \ref{lemma:small}}
From the definition of DIG, we know that for any $R_k\not\in\mathcal{PA}_j$, 
$
 I(R_k\rightarrow R_j||\mathcal{R}_{-\{k,j\}})=0   
$. 
This implies that for all $t$, 
\begin{align}\label{eq:app_l1}
     p(R_{j,t}|\mathcal{R}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{k\}}^{t-1}).
\end{align}
On the other hand, by the assumption of the Lemma, $R_i\not\in\mathcal{PA}_j$, we have
\begin{align}\label{eq:app_ll2}
 I(R_i\rightarrow R_j||\mathcal{R}_{-\{i,j\}})=0,  
\end{align}
or equivalently, for all $t$,
\begin{align}\label{eq:app_p1}
     p(R_{j,t}|\mathcal{R}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1}).
\end{align}
 Combining \eqref{eq:app_l1} and \eqref{eq:app_p1} imply that for any pair $\{R_i,R_k\}$ that are not in the parent set of $R_j$, we have
\begin{align}\label{eq:app_l1_2}
   p(R_{j,t}|\mathcal{R}_{-\{k\}}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1}).
\end{align}
To prove the claim of this lemma, we use \eqref{eq:app_l1_2} to show that all the time series in $\mathcal{R}_{-\{i,j\}}\setminus\mathcal{C}$ can be removed from the conditioning in \eqref{eq:app_ll2}. 
Let $R_k\in \mathcal{R}_{-\{i,j\}}\setminus\mathcal{C}$, by multiplying the above equality with $p(R_{i}^{t-1}|\mathcal{R}_{-\{i,k\}}^{t-1})$ and marginalizing over $R_{i}^{t-1}$, we obtain
\begin{align*}
    &\int p(R_{j,t}|\mathcal{R}_{-\{k\}}^{t-1})p(R_{i}^{t-1}|\mathcal{R}_{-\{i,k\}}^{t-1})dR_i^{t-1}=p(R_{j,t}|\mathcal{R}_{-\{i,k\}}^{t-1})\\
    &=\int p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1})p(R_{i}^{t-1}|\mathcal{R}_{-\{i,k\}}^{t-1})dR_i^{t-1}=p(R_{j,t}|\mathcal{R}_{-\{i\}}^{t-1}).
\end{align*}
The above equalities and \eqref{eq:app_p1} imply that for all $t$,
\begin{align*}
p(R_{j,t}|\mathcal{R}^{t-1})=p(R_{j,t}|\mathcal{R}_{-\{i,k\}}^{t-1}),    
\end{align*}
or equivalently,  
\begin{align*}
    I(R_i\rightarrow R_j||\mathcal{R}_{-\{i,j,k\}})=0.
\end{align*}
By repeating the above procedure, we obtain
\begin{align*}
    I(R_i\rightarrow R_j||\mathcal{C})=0.
\end{align*}

\subsubsection{Proof of Lemma \ref{lemma:lin}}
Consider the VAR model in \eqref{eq:linearsys}. 
First, we assume that $X_i$ has no influence on $X_j$, i.e., $I(X_i\rightarrow X_j||\mathcal{X}_{-\{i,j\}})=0$ or equivalently $a_{j,i}=0$ and show that \eqref{eq:lemma_linear} holds. Given this assumption, we have that for all $t$,
\begin{align*}
    &p(X_{j,t}|\mathcal{X}_{-\{i\}}^{t-1})=p(X_{j,t}|\mathcal{X}^{t-1}).
\end{align*}
Using the equations in \eqref{eq:linearsys} and the assumption that $a_{j,i}=0$, we obtain
\begin{align*}
    &p(X_{j,t}|\mathcal{X}^{t-1})= p(N_{j,t}+\sum_{k}a_{j,k}X_{k,t-1}|\mathcal{X}^{t-1})=p(N_{j,t}+\sum_{k\neq i}a_{j,k}X_{k,t-1}|\mathcal{X}^{t-1})\\ 
    &=p(N_{j,t}+\sum_{k\neq i}a_{j,k}X_{k,t-1}|\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{i}^{t-1},{X}_{j}^{t-1})\\
    &=p(N_{j,t}+\sum_{k\neq i}a_{j,k}X_{k,t-1}|\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{j}^{t-1}).
\end{align*}
Note that we could replace $\mathcal{X}^{t-1}$ by $\{\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{i}^{t-1},{X}_{j}^{t-1}\}$ or\\
$\{\sum_{k\neq i}a_{j,k}X_{k,t-1},{X}_{j}^{t-1}\}$ in the above equations, because given either of them $\sum_{k\neq i}a_{j,k}X_{k,t-1}$ becomes a constant and independent of $N_{j,t}$.
By defining $Q_{t-1}:=\sum_{k\neq i}a_{j,k}X_{k,t-1}$, the above equations can be rewritten as follows 
\begin{align*}
    &p(X_{j,t}|\mathcal{X}^{t-1})=p(X_{j,t}|Q_{t-1},{X}_{i}^{t-1},{X}_{j}^{t-1})=p(X_{j,t}|Q_{t-1},{X}_{j}^{t-1}), \forall t,
\end{align*}
or equivalently, 
\begin{align*}
    &\mathbb{E}\left[\log\frac{p(X_{j,t}|Q_{t-1},{X}_{i}^{t-1},{X}_{j}^{t-1})}{p(X_{j,t}|Q_{t-1},{X}_{j}^{t-1})}\right]=0, \forall t.
\end{align*}
Using the definition of DI, the above equalities can be written in terms of DI as follows
\begin{align*}
   I(X_i\rightarrow X_j||Q)=0.
\end{align*}
On the other hand, we have 
\begin{align*}
&[a_{j,1},...,a_{j,i-1},a_{j,i+1},...,a_{j,m}]=\arg\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||X_{j,t}- \textbf{w}^T \textbf{X}_{-\{i\},t-1}||_2^2\right]:=\textbf{u}_t.
\end{align*}
where $\textbf{X}_{-\{i\},t-1} :=[X_{1,t-1},..., X_{i-1,t-1}, X_{i+1,t-1},..., X_{m,t-1} ]^T$. This means that $Q_{t-1}=\textbf{u}_t^T\textbf{X}_{-\{i\},t-1}$.

@@

\subsubsection{Proof of Lemma \ref{lemma:nonlinear}}
The proof is similar to the linear version and uses the fact that exogenous noises $\{\varepsilon_{j,t}\}$ are independent. More precisely, we have  
\begin{align*}
    &p(X_{j,t}|\mathcal{X}^{t-1})=p(F_{j}(\mathcal{X}^{t-1}) + \varepsilon_{j,t}|F_{j}(\mathcal{X}^{t-1})).
\end{align*}
Since there is no influence from $X_i$ to $X_j$, we can eliminate it from the conditioning and the argument of function $F_j$ and obtain
\begin{align*}
&p\big(F_{j}(\mathcal{X}^{t-1}) + \varepsilon_{j,t}|\mathcal{X}^{t-1}\big)=p\big(F_{j}(\mathcal{X}_{-\{i\}}^{t-1}) + \varepsilon_{j,t}|\mathcal{X}_{-\{i\}}^{t-1}\big).
\end{align*}
On the other hand, because given either $\{F_{j}(\mathcal{X}_{-\{i\}}^{t-1}), X_i^{t-1},X_j^{t-1}\}$ or \\
$\{F_{j}(\mathcal{X}_{-\{i\}}^{t-1}),X_j^{t-1}\}$, the value of $F_{j}(\mathcal{X}_{-\{i\}}^{t-1})$ is no longer a random variable. Using this relationship and the fact that $\varepsilon_{j,t}$ is independent of $\mathcal{X}^{t-1}$, we obtain
\begin{small}
\begin{align*}
    &p\big(F_{j}(\mathcal{X}_{-\{i\}}^{t-1}) + \varepsilon_{j,t}|F_{j}(\mathcal{X}_{-\{i\}}^{t-1}), X_i^{t-1},X_j^{t-1}\big)=
    p\big(F_{j}(\mathcal{X}_{-\{i\}}^{t-1}) + \varepsilon_{j,t}|F_{j}(\mathcal{X}_{-\{i\}}^{t-1}), X_j^{t-1}\big).
\end{align*}
\end{small}
By defining $Q_{t-1}:=F_{j}(\mathcal{X}_{-\{i\}}^{t-1})$, the above equations can be rewritten in terms of DI as follows,
\begin{align*}
    I(X_i\rightarrow X_j||Q)=0.
\end{align*}

@@

\subsection{k-Nearest Neighbors estimator of mutual information}
Suppose that $N+M$ i.i.d. realizations $\{\textbf{x}_1, ..., \textbf{x}_{N+M}\}$ are available from $\PP_{X,Y,Z}$, where $\textbf{x}_i$ denotes the $i$-th realization of $(X,Y,Z)$.
The data is randomly divided into two subsets $\mathcal{S}_1$ and $\mathcal{S}_2$ of $N$ and $M$ points, respectively.  
The estimator has two main stages:
In the first stage, a k-nearest density estimator $\widehat{\PP}_{X,Y,Z}$ at the $N$ points of $\mathcal{S}_1$ is estimated using the $M$ realizations of $\mathcal{S}_2$ as follows:

@@

\subsection{Koopman-based Lifting Method}
Let $\textbf{X}_t:=\{X_{1,t}, ..., X_{m,t}\}$ denote a network of $m$ time series such that 
\begin{align}\label{dyn}
\dot{\textbf{X}}_t = F(\textbf{X}_t),
\end{align}
where the vector field $F(\textbf{X})=(F_1(\textbf{X}),...,F_m(\textbf{X}))$ is of the form
\begin{align}
F_j(\textbf{X})= \sum_{k=1}^K w_{j,k} h_k(\textbf{X}).
\end{align}
In the above equation, $w_{j,k}\in\mathbb{R}$ are unknown weights and $\{h_k(\textbf{X})\}$ denote a set of known library functions, e.g., monomials. 
Furthermore, let $\varphi^t(\textbf{X}_0)$ denote the solution to \eqref{dyn} associated with the initial condition $\textbf{X}_0$.

@@

\subsection{Ideal portfolio}
In this section, we show how the ideal portfolio is related to the coefficients of the linear system in \eqref{eq:linearsys}.  
Recall the optimization problem in Lemma \ref{lemma:lin}. 
\begin{align*}
&\textbf{u}_t:=\arg\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||X_{j,t}- \textbf{w}^T \textbf{X}_{-\{i\},t-1}||_2^2\right],\\
&\textbf{X}_{-\{i\},t-1} :=[X_{1,t-1},\cdots, X_{i-1,t-1}, X_{i+1,t-1}, \cdots, X_{m,t-1} ]^T.
\end{align*}
Consider the $j$-th Equation in \eqref{eq:linearsys}, i.e., 
\begin{align*}
    X_{j,t}=\sum_{k=1}^m a_{j,k}X_{k,t-1}+N_{j,t}.
\end{align*}
If $a_{j,i}=0$, by substituting the above equation into the optimization, we obtain
\begin{align*}
&\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}+N_{j,t}||_2^2\right]=\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||N_{j,t}||_2^2\right]\\
&+\mathbb{E}\left[||\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}||_2^2\right]+2\mathbb{E}\left[||\left(\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}\right)N_{j,t}||_2^2\right]\\
&=\min_{\textbf{w}\in\mathbb{R}^{m-1}}\mathbb{E}\left[||\sum_{k\neq i} (a_{j,k}-w_{k})X_{k,t-1}||_2^2\right]+\mathbb{E}\left[||N_{j,t}||_2^2\right]
\end{align*}
The last equality is due to the fact $N_{j,t}$ is independent of $\{X_{k,t-1}\}$ and have zero mean. This implies that the solution is $w_k=a_{j,k}$ for $k\in\{1,...,i-1,i+1,...,m\}$.

\begin{comment}
\subsection*{Appendix D : Ideal portfolio}
In this section, we present the relation between the ideal portfolio defined in Lemma \ref{lemma:lin} and maximally correlated portfolio. 
We use the following notations and definitions,
\begin{itemize}
\item $r$ denotes the risk-free return (random, but known at beginning of period),
  %\item $X_j$ denotes the excess return of stock $j$ over risk-free $r$,
  \item Candidate excess returns $\textbf{R}=(R_1,\dots,R_{m-1})^T$ over risk-free $r$,
  %(all stocks but $i$ and $j$, e.g., $m=498$)
  \item Covariance matrix of $\begin{pmatrix}
    X \\ \textbf{R}
  \end{pmatrix}$ is denoted by $\mathbf{\Sigma}:=\begin{pmatrix}
    \mathbf{\Sigma}_{XX} & \mathbf{\Sigma}_{X\textbf{R}} \\ \mathbf{\Sigma}_{\textbf{R}X} & \mathbf{\Sigma}_{\textbf{RR}}
  \end{pmatrix}  $. We assume that $\mathbf{\Sigma}_{\textbf{RR}}$ is invertible.

@@

\section{Appendix to Chapter 3}
\subsection{Number of messages}
As the same information sometimes refer to several companies, users are allowed to identify more than one ticker per message.  Figure \ref{fig:histtic} shows the histogram of the number of tickers tagged per message. As the vast majority of message includes only one ticker, we only show on this plot messages referring to more than one ticker. However, many messages refer to several tickers and this creates duplicates in the database because we consider the same message for all tickers tagged in the message. Figure \ref{fig:uniq} shows the number of messages with and without double counting. In our sample, the number of messages without double counting is 76 million, as opposed to 90 million messages with double counting. Figure \ref{fig:ratio} shows the ratio between the number of messages with double counting divided by the number of messages without double counting. Throughout this paper, we only refer to the number of messages with double counting.

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{hist_tic.JPG}
    \mycaption{Number of tickers per message}{Histogram of the number of tickers per message, across all messages referring to more than one ticker. The maximum number of tickers per message amounts to 28 and corresponds to 11 messages in the sample.}
    \label{fig:histtic}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{uniq.JPG}
    \mycaption{Number of messages}{Total number of messages with double counting (red) compared to the total number of messages without double counting (blue). Numbers are aggregated daily.}
    \label{fig:uniq}
\end{figure}
